---
title: "R Notebook"
output: html_notebook
---
Import Libraries: 
```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(readr)
library (visdat)
library(superml)
library(plyr)
library(factoextra)
```

Import data file & preview data: 
```{r}
df <- read_csv('/Users/Amanda.Hartzler/Desktop/Data_Analytics_Masters/D207/churn_clean.csv')
head(df)
```

Create a contingency/two-way table with the Churn & TechSupport variables.
```{r}
table(df$Churn, df$TechSupport) #(Soetewey, 2020)
```

Create Barplot to visually represent the data. 
```{r}
ggplot(df) +
  aes(x = Churn, fill = TechSupport) +
  geom_bar(position = "dodge")
#(Soetewey, 2020)
```
Chi-Square Test: 
```{r}
test <- chisq.test(table(df$Churn, df$TechSupport))
test
#(Soetewey, 2020)
```

Create Income Histogram:
```{r}
hist(df$Income, 
     main = 'Annual Income of Customers', 
     xlab = 'Annual Income (US Dollars $)', 
     border = 'black', 
     col = '#044da4', 
     xaxp=c(0,250000,10))
abline(h=seq(0,5000,1000), col="gray", lty="dotted" )
#(Palay, 2015)
```

Summary of Income Column:
```{r}
summary(df$Income)
```

Create Outage_sec_perweek Histogram: 
```{r}
hist(df$Outage_sec_perweek, 
     main = 'Outage Seconds Per Week for Customers', 
     xlab = 'Outage Per Week (Seconds)', 
     border = 'black',
     col = '#a75a12',
     breaks = seq(0,25,2.5),  
     xaxp = c(0,25,5))
abline(h=seq(0,3000,500), col="gray", lty="dotted" )
#(Palay, 2015)
```
Summary of Outage_sec_perweek Column:
```{r}
summary(df$Outage_sec_perweek)
```

Create Bar Chart of InternetService:
```{r}
counts <- table(df$InternetService)
barplot(counts, main="Distribution of Internet Service Types",
   xlab="Internet Service Types", 
   ylab="Count", 
   border = 'black',
   col = '#0e6d05')
abline(h=seq(0,4000,1000), col="gray", lty="dotted" )
```

Summary of InternetService Column:
```{r}
table(df$InternetService)
#(2021)
```

Create Bar Chart of Contract:
```{r}
counts <- table(df$Contract)
barplot(counts, main="Type of Customer Contracts Distribution",
   xlab="Type of Contract", 
   ylab="Count", 
   border = 'black',
   col = '#6d0691')
abline(h=seq(0,5000,1000), col="gray", lty="dotted" )
```

Summary of Contract Column:
```{r}
table(df$Contract)
#(2021)
```

Scatterplot of Income vs Outage_sec_perweek:
```{r}
attach(df)
plot(Income, Outage_sec_perweek, main="Annual Income vs. Outage per Week",
   xlab="Annual Income (US Dollars $)", ylab="Average Outage per Week (Seconds)",
   col = '#91060f', pch=19)
#(Kabakoff, 2017)
```

Create Barplot of InternetService vs. Contract:
```{r}
ggplot(df) +
  aes(x = InternetService, fill = Contract) +
  geom_bar(position = "dodge")
#(Soetewey, 2020)
```
